\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-16 report/article_4.tex
start tidyup
latex report expansion

% \begin{figure}[h!]
% \begin{center}
% \includegraphics[width=.1\textwidth]{Figures/logo.png} \\
% \includegraphics[scale=.12]{Figures/logotext.png} \\
% \caption*{ {\sf Democratising real estate investment}}
% \end{center}
% \end{figure}

@@

>>>>

\clearpage

\section*{Summary}

In this report I've given a brief overview my attempts to elute maximal
insight from a single large dataset through the data science techniques of
visualisation and quantitative modelling. Together they form a
cohesive narrative of investigative analysis into a single exemplar
postcode, and discovery of the potential investment returns
therein.

These analyses have to potential to generate valuable insights for a range of
customer segments:
\begin{itemize}

\item Online sales and letting agents would benefit from
plug-in analytics provided by \logo \hspace{.1em} --- offering their
users advanced insights into spatiotemporal property statistics.

\item A web and mobile app to make a set of analyses widely-available
  to amateur property investors, new homebuyers and landlords.

\item A consultancy specialising in real estate investment to partner
  with REITs and other specialist investment funds, as well as charitable trusts.
\end{itemize}

@@

\vspace{2em}
\begin{figure}[h!]
\begin{center}
\includegraphics[width=.15\textwidth]{Figures/logo.png} \\
\includegraphics[scale=.12]{Figures/logotext.png} \\
\caption*{ {\sf Democratising real estate investment}}
\end{center}
\end{figure}
